---
title: "Group-Project-Update1"
author: "Kossi Akplaka"
date: "2023-10-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an update on how to clean the column title. I'll create a new column called new_title based on the description.

For this following job title, I'll look for this following keywords in the description column:

- data engineer: ETL, pipelines, warehouse, architect

- data science: Machine learning, modeling, A/B testing

- data analyst: All other

If a job description contains both "data analyst" and "data science" keywords, the code will categorize it based on the first condition that matches.

## Import the data

I can import the data from github. 

```{r}
library(dplyr)

df <- read.csv('https://raw.githubusercontent.com/Group-Project-Data-607/Project3/main/Data_Science_job.csv')
df
```

## Make a new_title

```{r}
title_df <- df %>%
  mutate(new_title = case_when(
    grepl("ETL|pipeline|warehouse|architect", description, ignore.case = TRUE) ~ "Data Engineer",
    grepl("machine learning | modeling|A/B testing", description, ignore.case = TRUE) ~ "Data Science",
    TRUE ~ "Data analysis"
  )) %>% 
  select(title, description, new_title)
```

## Count of the different title

```{r}
table(title_df$new_title)
```

